Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-22 Draft/draft.tex
Honghao: more on robustness
Honghao: a more promising way to apply the isometry; a more complete self-testing proof

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=1$}&
\multicolumn{3}{|c|}{$x=2$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
\cline{2-8}
&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
\hline
\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
\cline{2-8}
&$b=1$ & $\frac{\sin^2(\pi/2d)}{d-1}$ & $\frac{\cos^2(\pi/2d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x,y \in [2]$.}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=1$}&
\multicolumn{3}{|c|}{$x=2$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/(d-1)$ & $1/(d-1)$ & 0 
& $1/(d-1)$ & $1/(d-1)$ & 0 \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
&  0 & 0 & \small $\frac{d-3}{d-1} $  \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
\end{table}
Alice's projectors are 
\begin{align*}
	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
	&A_1^0 = \ketbra{u_1}{u_1}, A_1^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_1^\perp = \Pi_V^\perp\\
	&A_2^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
	A_2^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_2^\perp = \Pi_V^\perp.
\end{align*}
Bob's projectors are 
\begin{align*}
	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
	&B_1^0|_V = \left( \cos(\frac{\pi}{2d})\ket{u_1} + \sin(\frac{\pi}{2d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{2d})\bra{u_1} + \sin(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
	&B_1^1|_V = \left( \sin(\frac{\pi}{2d})\ket{u_1} - \cos(\frac{\pi}{2d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{2d})\bra{u_1} - \cos(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
	&B_2^0|_V = \left( \cos(\frac{\pi}{2d})\ket{u_1} - \sin(\frac{\pi}{2d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{2d})\bra{u_1} - \sin(\frac{\pi}{2d})\bra{u_{d-1}}\right)\\
	&B_2^1|_V = \left( \sin(\frac{\pi}{2d})\ket{u_1} + \cos(\frac{\pi}{2d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{2d})\bra{u_1} + \cos(\frac{\pi}{2d})\bra{u_{d-1}}\right).
\end{align*}
About Bob's projectors for input $y \in [2]+1$, we are only interested in their actions when restricted 
to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.

@@

The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
We give steps about how $\Phi_A$ and $\Phi_B$ works.
Since the subspaces $W_j$'s are orthogonal, Alice and Bob can map state $\ket{\psi}$ to the state 
\begin{align}
	\ket{\psi'} = \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{j}_A\ket{j}_B.
\end{align}
Note that we added subscript $A$ and $B$ to stress the subsystems holden by Alice and Bob respectively.
Since $\ket{x_{i,j}}$ is orthogonal to $\ket{x_{i',j'}}$ for $i\neq i'$ or $j \neq j'$, we further assume that there exists 
a unitary $O$ such that $O\ket{x_{i,j}} = O\ket{x_{i,j+1}}$ for all $i$ and $j$, but when $j = N$, $O\ket{x_{i,N}} = \ket{x_{i,1}}$.
Then controlled by the appended register, Alice and Bob can apply $(O\ct)^j$ to the original system
and $\ket{\psi'}$ is mapped to
\begin{align}
	 &\sum_{i=1}^{d-1}\sum_{j=1}^m c_j [(O\ct)^j\ket{x_{i,j}}_A] \x [(O\ct)^j\ket{x_{i,j}}_B] \x \ket{j}_A\ket{j}_B\\
	 = &\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,1}}_A\ket{x_{i,1}}_B \ket{j}_A\ket{j}_B\\
	 =  &\frac{1}{\sqrt{d}} \sum_{i=1}^{d-1} \ket{x_{i,1}}_A\ket{x_{i,1}}_B \x \sum_{j=1}^m \sqrt{d}c_j \ket{j}_A\ket{j}_B
\end{align}
After relabelling $\ket{x_{i,1}}$ as $\ket{i}$, we factor $\ket{\EPR{d-1}}$ out of $\Phi_A \x \Phi_B \ket{\psi}$.
\end{proof}
%The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
%\begin{align}
%	X \ket{x_i} = \omega_d^i \ket{x_i}.
%\end{align}
%The other effect of $\SVT_X$ is that we know 
%\begin{align}
%	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
%\end{align}
%\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
In summary, for any odd prime number $d$ whose primitive root is $2$,$3$ or $5$, 
\cref{prop:realize} tells us that the correlation $C(d)$ is achievable by a quantum strategy 
and \cref{thm:selftest} tells us that the correlation $C(d)$ can self-test the EPR pair of
local dimension $d-1$. Moreover, there are infinitely many prime numbers
whose primitive root is in the set $\{2,3,5\}$ \cite{murty1988},
Hence, our main result is the following theorem.
\begin{theorem}
	There exists an infinity-sized set $D$ of prime numbers such that 
	each $d \in D$ has primitive root $2$, $3$ or $5$ and there exists
	a constant-sized correlation $C(d)$ that can self-test the EPR pair of 
	local dimension $d-1$.
\end{theorem}
We remark that our proof works for any odd prime number with primitive root $r$.
However, since there is no upper-bound of $r$ for a general prime number $d$, we 
cannot claim the corresponding correlation $C(d)$ is constant-sized. On the other
hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
way to test EPR pairs of prime local dimension than the one proposed in Ref.~\cite{cgs2017}.
The size of our correlation grows linearly in $r$ whereas the Coladangelo \textit{et. al.}'s
method uses correlation grows linearly in $d$.

>>>>

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=1$}&
\multicolumn{3}{|c|}{$x=2$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{\sin^2(\pi/d)}{d-1}$ & \small $\pr{\perp0}{00}$ 
& $\frac{1+\sin(\pi/d)}{2(d-1)}$ & $\frac{1-\sin(\pi/d)}{2(d-1)}$ & \small  $\pr{\perp0}{10}$ \\
\cline{2-8}
&$b=1$ & $\frac{\sin^2(\pi/d)}{d-1}$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{d-3}{d-1}-\pr{\perp0}{00}$ 
&  $\frac{1-\sin(\pi/d)}{2(d-1)}$ & $\frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1} - \pr{\perp0}{10}$  \\
\hline
\multirow{2}{*}{$y = 2$} & $b=0$ & $\frac{\cos^2(\pi/d)}{d-1}$ & $\frac{\sin^2(\pi/d)}{d-1}$ & \small $\pr{\perp0}{01}$ & 
$ \frac{1-\sin(\pi/d)}{2(d-1)}$ & $ \frac{1+\sin(\pi/d)}{2(d-1)}$ & \small $\pr{\perp 0}{11}$  \\
\cline{2-8}
&$b=1$ & $\frac{\sin^2(\pi/d)}{d-1}$ & $\frac{\cos^2(\pi/d)}{d-1}$ & \small $\frac{d-3}{d-1}-\pr{\perp0}{01}$ &  
$ \frac{1+\sin(\pi/d)}{2(d-1)}$ & $ \frac{1-\sin(\pi/d)}{2(d-1)}$ & \small $\frac{d-3}{d-1}- \pr{\perp 0}{11}$ \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x,y \in [2]$.}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=1$}&
\multicolumn{3}{|c|}{$x=2$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/(d-1)$ & $1/(d-1)$ & 0 
& $1/(d-1)$ & $1/(d-1)$ & 0 \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $\frac{d-3}{d-1}$ 
&  0 & 0 & \small $\frac{d-3}{d-1} $  \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
\end{table}
Alice's projectors are 
\begin{align*}
	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
	&A_1^0 = \ketbra{u_1}{u_1}, A_1^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_1^\perp = \Pi_V^\perp\\
	&A_2^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
	A_2^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_2^\perp = \Pi_V^\perp.
\end{align*}
Bob's projectors are 
\begin{align*}
	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
	&B_1^0|_V = \left( \cos(\frac{\pi}{d})\ket{u_1} + \sin(\frac{\pi}{d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{d})\bra{u_1} + \sin(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
	&B_1^1|_V = \left( \sin(\frac{\pi}{d})\ket{u_1} - \cos(\frac{\pi}{d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{d})\bra{u_1} - \cos(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
	&B_2^0|_V = \left( \cos(\frac{\pi}{d})\ket{u_1} - \sin(\frac{\pi}{d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{d})\bra{u_1} - \sin(\frac{\pi}{d})\bra{u_{d-1}}\right)\\
	&B_2^1|_V = \left( \sin(\frac{\pi}{d})\ket{u_1} + \cos(\frac{\pi}{d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{d})\bra{u_1} + \cos(\frac{\pi}{d})\bra{u_{d-1}}\right).
\end{align*}
About Bob's projectors for input $y \in [2]+1$, we are only interested in their actions when restricted 
to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.

@@

The last step is to construct the local isometries $\Phi_A$ and $\Phi_B$ that can produce $\ket{\EPR{d-1}}$ from $\ket{\psi}$.
To help understanding, we draw a diagram to demonstrate the isometry first and then show
how this isometry works.
    	node[midway,left] (bracket1) {$\ket{\psi}$}
        \node[operator] (op11) at (1,0) {$QFT_d$} edge [-] (q1);
        \node[operator] (op14) at (1,-3) {$QFT_d$} edge [-] (q4);
	\node[operator] (op22) at (2,-1) {$X_A$} edge [-] (q2);
	\node[operator] (op23) at (2, -2) {$X_B$} edge[-] (q3);
        \node[operator] (op31) at (3,0) {$QFT_d^{-1}$} edge [-] (phase11);
        \node[operator] (op34) at (3,-3) {$QFT_d^{-1}$} edge [-] (phase14);
	\node[operator] (op42) at (4,-1) {$U_A$} edge [-] (op22);
	\node[operator] (op43) at (4, -2) {$U_B$} edge[-] (op23);
    	node[midway,right] (bracket2) {$\ket{\EPR{d-1}}$}
The isometry maps the state $\ket{\psi}$ in the following steps:
\begin{enumerate}
	\item Append $\ket{0}_A$ on Alice's side and $\ket{0}_B$ on Bob's side as control registers, and
	the state becomes $\ket{\psi} \ket{0}_A \ket{0}_B$;
	\item Apply $QFT_d$ to the control registers, and the state becomes
		\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \ket{\psi} \ket{k_1}_A \ket{k_2}_B;
	\item Apply $X_A^{k_1}$ to Alice's share of $\ket{\psi}$ and $X_B^{k_2}$ to Bob's share controlled
	by the control registers, and the state becomes
		&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1}X_A^{k_1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B\\
		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1}\ket{x_{i,j}}_A X_B^{k_2}\ket{x_{i,j}}_B
		\ket{k_1}_A \ket{k_2}_B\\
		=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1i+k_2i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
		\ket{k_1}_A \ket{k_2}_B;
	\item Apply $QFT_d^{-1}$ to the control registers, and the state becomes
		&\frac{1}{d^2} \sum_{l_1,l_2 =0}^{d-1}\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i-l_1)+k_2(i-l_2)} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
		\ket{l_1}_A \ket{l_2}_B\\
		=& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B;
	\item Let $n_i$ satisfy the condition $r^{n_i} \equiv i \pmod{d}$, apply $U_A^{(i)} = U_A^{n_i}$ to Alice's share of $\ket{\psi}$ and $U_B^{(i)} = U_B^{n_i}$ to Bob's share controlled
	by the control registers, and the state becomes
		&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B \\
		=&\sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i r^{-n_i} ,j}}_A \ket{x_{i r^{-n_i},j}}_B \ket{i}_A\ket{i}_B\\
		=& \sum_{i=1}^{d-1} \sum_{j=1}^m c_j \ket{x_{i i^{-1},j}}_A \ket{x_{i i^{-1},j}}_B \ket{i}_A\ket{i}_B\\
		= &\left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \sum_{i=1}^{d-1} \ket{i}_A\ket{i}_B\\
		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
		\frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1}\ket{i}_A\ket{i}_B\\
		=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \ket{\EPR{d-1}},
	where in the last line we used the fact that $\norm{\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B} = 1/\sqrt{d-1}$.
\end{enumerate}

If the initial state is $X_A\ket{\psi}$, the isometry maps the state as following
\begin{align}
	X_A\ket{\psi} \to &X_A\ket{\psi}\ket{0}_A\ket{0}_B\\
	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} X_A^{k_1+1} X_B^{k_2}\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1+k_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
		\ket{k_1}_A \ket{k_2}_B\\
	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i\omega_d^{(k_1-l_1)i+(k_2-l_2)i} \ket{x_{i,j}}_A\ket{x_{i,j}}_B
		\ket{l_1}_A \ket{l_2}_B\\
	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{i,j}}_A\ket{x_{i,j}}_B \ket{i}_A \ket{i}_B\\
	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i U_A^{(i)}\ket{x_{i,j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^i \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{i}_A\ket{i}_B\\
	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\omega_d^i \ket{i}_A\ket{i}_B\\
	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tX_A \ket{\EPR{d-1}},
\end{align}
where $\tX_A$ is the ideal $X$ operator.
The case of $X_B\ket{\psi}$ is similar, so we omit it here.

If the initial state is $U_A\ket{\psi}$, the isometry maps the state as following
\begin{align}
	U_A\ket{\psi} \to &U_A\ket{\psi}\ket{0}_A\ket{0}_B\\
	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} U_A\ket{\psi} \ket{k_1}_A \ket{k_2}_B \\
	= &\frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A\ket{x_{i,j}}_A\ket{x_{i,j}}_B
		\ket{k_1}_A \ket{k_2}_B\\
	= & \frac{1}{d} \sum_{k_1,k_2=0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{i r^{-1} ,j}}_A\ket{x_{i,j}}_B
		\ket{k_1}_A \ket{k_2}_B\\
	\to &\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j X_A^{k_1} \ket{x_{i r^{-1} ,j}}_A
	X_B^{k_2}\ket{x_{i,j}}_B  \ket{k_1}_A \ket{k_2}_B \\
	=&\frac{1}{d} \sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1 i/r}\omega_d^{k_2i} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
		\ket{k_1}_A \ket{k_2}_B\\
	\to &\frac{1}{d^2}\sum_{k_1,k_2 =0}^{d-1} \sum_{i=1}^{d-1}\sum_{j=1}^m c_j \omega_d^{k_1(i/r-l_1)}\omega_d^{(k_2(i-l_2)} \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B
		\ket{l_1}_A \ket{l_2}_B\\
	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j  \ket{x_{ir^{-1},j}}_A\ket{x_{i,j}}_B \ket{ir^{-1}}_A \ket{i}_B\\
	\to& \sum_{i=1}^{d-1}\sum_{j=1}^m c_j U_A^{(ir^{-1})}\ket{x_{ir^{-1},j}}_A U_B^{(i)}\ket{x_{i,j}}_B \ket{i}_A\ket{i}_B\\
	=&\sum_{i=1}^{d-1}\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B \ket{ir^{-1}}_A\ket{i}_B\\
	=&\sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x 
		\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1}\ket{ir^{-1}}_A\ket{i}_B\\
	=& \sqrt{d-1} \left(\sum_{j=1}^m c_j \ket{x_{1,j}}_A \ket{x_{1,j}}_B\right) \x \tU_A \ket{\EPR{d-1}},
\end{align}
where $\tU_A$ is the ideal $U$ operator on Alice's side.
The derivation is similar when $U_B$ is applied, so we omit it here.
\end{proof}
%The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
%\begin{align}
%	X \ket{x_i} = \omega_d^i \ket{x_i}.
%\end{align}
%The other effect of $\SVT_X$ is that we know 
%\begin{align}
%	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
%\end{align}
%\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}
In summary, for any odd prime number $d$ whose primitive root is $2$,$3$ or $5$, 
\cref{prop:realize} tells us that the correlation $C(d)$ is achievable by a quantum strategy 
and \cref{thm:selftest} tells us that the correlation $C(d)$ can self-test the EPR pair of
local dimension $d-1$. Moreover, there are infinitely many prime numbers
whose primitive root is in the set $\{2,3,5\}$ \cite{murty1988},
Hence, our main result is the following theorem.
\begin{theorem}
	There exists an infinity-sized set $D$ of prime numbers such that 
	each $d \in D$ has primitive root $2$, $3$ or $5$ and there exists
	a constant-sized correlation $C(d)$ that can self-test the EPR pair of 
	local dimension $d-1$.
\end{theorem}
We remark that our proof works for any odd prime number with primitive root $r$.
However, since there is no upper-bound of $r$ for a general prime number $d$, we 
cannot claim the corresponding correlation $C(d)$ is constant-sized. On the other
hand, since $r$ is usually much smaller than $d$, our result implies a more efficient
way to test EPR pairs of prime local dimension than the one proposed in Ref.~\cite{cgs2017}.
The size of our correlation grows linearly in $r$ whereas the Coladangelo \textit{et. al.}'s
method uses correlation grows linearly in $d$.
